\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-25 OaklandSubmission/ld.tex
ld

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{add}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced?}}
\label{fig:circuits}
\end{figure}

>>>>

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{add}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced?}}
\label{fig:circuits}
\end{figure}
